Erratum: Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae [Phys.~Rev.~D 105, 063006 (2021)]

### 2021-11-02 erratum/ccsn_erratum.tex
Erratum

\title{Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae}

@@

\begin{abstract}
The eventual detection of gravitational waves from core-collapse supernovae (CCSN) will help improve our current understanding of the explosion mechanism of massive stars. The stochastic nature of the late post-bounce gravitational wave signal due to the non-linear dynamics of the matter involved and the large number of degrees of freedom of the phenomenon make the source parameter inference problem very challenging. In this paper we take a step towards that goal and present a parameter estimation approach which is based on the gravitational waves associated with oscillations of proto-neutron stars (PNS). Numerical simulations of CCSN have shown that buoyancy-driven g-modes are responsible for a significant fraction of the gravitational wave signal and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations, as demonstrated in~\citep{Torres:2019b}. We use a set of 1D CCSN simulations to build a model that relates the  evolution of the PNS properties with the frequency of the dominant g-mode, which is extracted from the gravitational-wave data using a new algorithm we have developed for our study. The model is used to infer the time evolution of a combination of the mass and the radius of the PNS. The performance of the method is estimated employing simulations of 2D CCSN waveforms covering a progenitor mass range between 11 and 40 solar masses and different equations of state. Considering signals embedded in Gaussian gravitational wave detector noise, we show that it is possible to infer PNS properties for a galactic source using Advanced LIGO and Advanced Virgo data at design sensitivities. Third generation detectors such as Einstein Telescope and Cosmic Explorer will allow to test distances of ${\cal O}(100\, {\rm kpc})$. %\tf{Caveats? Gaussian noise?}
% 
%  Core-collapse supernovae are very important phenomena in the Universe and their expected gravitational
%  waves emission is a promising tool to study the onset of the supernova explosion mechanism. The complexity
%  of the gravitational wave signal due to matter effects and the large degrees of freedom of the phenomena
%  makes the source parameter inference problem very challenging. In this paper, we have considered the
%  proto neutron star oscillation modes that carry out a large fraction of the gravitational wave signal and
%  whose frequency time evolution is linked to the system properties through universal relations as
%  demonstrated in ~\cite{Torres:2019b}. We have developed a simple algorithm to extract from the
%  gravitational wave data the frequency evolution of the gravity mode. A set of 1D core collapse
%  supernova simulations is used to build a model of evolution of the proto neutron star properties
%  with the gravity mode frequency. The model is then used to infer the time evolution of a combinaison of
%  the radius and mass of the proto neutron star. We have then estimated the performance of the method by
%  performing simulations with 2D core collapse supernova waveforms covering a progenitor mass range between
%  11 and 40 solar mass and different equations of state. We have shown that for Advanced LIGO and Advanced
%  Virgo detectors at design sensitivity it will be possible to infer proton neutron star properties for
%  a galactic source, while third generation detectors Einstein Telescope and Cosmic Explorer will allow
%  to test distances of several hundreds of kiloparsec.

\end{abstract}

@@

\input{introduction}\bigskip

\input{simulations}\bigskip

\input{methods}\bigskip

\input{results}\bigskip

\input{conclusion}\bigskip

\bigskip\noindent\textit{Acknowledgments.--} Work supported by the Spanish Agencia Estatal de Investigaci\'on (PGC2018-095984-B-I00), by the Generalitat Valenciana (PROMETEO/2019/071) and by the European Union’s Horizon 2020 research and innovation (RISE) programme (H2020-MSCA-RISE-2017 GrantNo. FunFiCO-777740).
N.C. acknowledges support from National Science Foundation grant PHY-1806990.
R.M. gratefully acknowledges support by the James Cook Fellowship from Government funding, administered by the Royal Society Te  Ap\={a}rangi. R.M. and P.M.-R. also acknowledge funding from  DFG Grant KI 1443/3-2 and thank the Centre for eResearch at the University of Auckland for their technical support.
P.C.-D. acknowledges the support of the Spanish {\it Ramon y Cajal} programme (RYC-2015-19074) supporting his research.
\begin{appendices}
\input{appendixA}
\end{appendices}
%\bibliographystyle{unsrt}
\bibliography{biblio}

>>>>

\title{Erratum: Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae [Phys.~Rev.~D 105, 063006 (2021)]}

@@

@@

There is a factor $2$ missing in the calculation of the ratio $r\equiv M_{\rm PNS}/R^2_{\rm PNS}$ in \cite{Bizouard2021}.  This only affects the scale in  
Figs 1 and 3 and the numerical values in table II. Those should be replaced by Fig.~\ref{fig:LMVAR} and \ref{fig:ratio} and 
Table~\ref{tab:model}. The conclusions of the paper remain unaffected.

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 18 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. We have not made the distinction between the different simulations since we are only interested in the relationship between the variables.
 \pcd{[RATIO SHOULD BE MULTIPLIED BY A FACTOR 2 IN THE PLOT]}
 }
 \label{fig:LMVAR}
\end{figure}

\begin{table}[h]
 \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 1.00 \times 10^{-06}$ & $2.12 \times 10^{-08}$ \\   
   $\beta_2$  &  $-8.22 \times 10^{-10}$ & $5.00 \times 10^{-11}$ \\
   $\beta_3$  &  $ 1.01 \times 10^{-12}$ & $2.70 \times 10^{-14}$ \\
   $\alpha_0$ &  $-1.02 \times 10^{+01}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.\pcd{[CORRECT NUMBERS IN THE TABLE. JUST A FACTOR 2 iIN ALL COEFFICIENTS?]}}\label{tab:model}
\end{table}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Comparison of the time evolution of the ratio $M_{\rm PNS}/R_{\rm PNS}^2$ estimated from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (shown by open triangles and by the 95\% confidence belt in grey) against the value derived from the PNS mass and radius given by the simulation code (shown by filled black circles). The size of the triangles are represented proportionally to the magnitude of the $\mbox{}^2 g_2$-mode frequency estimates. \pcd{[RATIO SHOULD BE MULTIPLIED BY A FACTOR 2 IN THE PLOT]}}
 \label{fig:ratio}
\end{figure}

\bibliographystyle{unsrt}
\bibliography{biblio}
